Geometrization of characters of tori over non-Archimedean local fields

### 2013-07-08 shanghai.tex
Make a title and made a new section for bounded character sheaves
Change the title if you like  . . .

% !TEX encoding = UTF-8 Unicode
\documentclass[11pt]{amsart}
\title[Short groovy title goes here]{Long groovy title goes here}
\usepackage[british]{babel}
\usepackage{datetime}
\date{\today}
\author{Clifton Cunningham}
\address{University of Calgary}
\email{cunning@math.ucalgary.ca}
\author{David Roe}
\address{Pacific Institute for the Mathematical Sciences at the University of Calgary}
\email{roed.math@gmail.com}
\usepackage[utf8]{inputenc}
\renewcommand{\baselinestretch}{1.2}
\usepackage[notcite,color]{showkeys}
\usepackage{hyperref}
\usepackage{geometry}
\usepackage{amsthm}
\usepackage{amsmath}
\usepackage{amssymb}
%\usepackage[shortalphabetic]{amsrefs}
\usepackage[alphabetic]{amsrefs}
\renewcommand\MR{\relax}
\usepackage{xypic}
\usepackage{textcomp}
\usepackage{mathrsfs}
\usepackage{yfonts}
\newcommand{\mathswab}[1]{\operatorname{\textswab{#1}}}
\usepackage[T1]{fontenc}
\usepackage{tikz}
\usetikzlibrary{shapes,arrows}
\usepackage{manfnt}

@@

The main result of this paper is a canonical isomorphism
\[
\CSiso{\mathswab{T}_d} 
\iso
\Hom_{< d}(T(K),\EEx)
\] 
between the Picard group of the category of character sheaves on
$\mathswab{T}_d$ and the group of characters $T(K) \to \EEx$ of
depth at most $d$.  Since these isomorphisms are compatible with
respect to $d$, we also .....  \Clifton{I'll come back to working on
  this when we're closer to being finished. I'd be just as happy if
  you took this cup from my lips, though.}  In particular, by
specializing to the case $T= \Gm{K}$ and by
choosing an isomorphism $\EE \approx \CC$ (unnatural though it may
be), we arrive at a model for the group of quasi-characters of
$K^\times$: the monoidal category of character sheaves on the
Greenberg transform of the Neron model of
$\Gm{K}$.

@@

@@

  The sequence of character groups is left-exact: by
  Proposition~\ref{prop:pullback}, it is dual to the exact sequence of
  abelian groups
  \begin{equation}\label{eq:pi0}
    \xymatrix{
      1 \ar[r] & G^0(\Fq) \ar[r] & G(\Fq) \ar[r] & \pi_0(G)(\Fq) \ar[r] & 0;
    }
  \end{equation}
  since $\Hom(\ - \ ,\EEx)$ is left-exact, the sequence of
  character groups is left exact.

>>>>

% !TEX encoding = UTF-8 Unicode
\documentclass[11pt]{amsart}
\title[Geometration of characters of tori]{Geometrization of characters of tori over non-Archimedean local fields}
\usepackage[british]{babel}
\usepackage{datetime}
\date{\today}
\author{Clifton Cunningham}
\address{University of Calgary}
\email{cunning@math.ucalgary.ca}
\author{David Roe}
\address{Pacific Institute for the Mathematical Sciences at the University of Calgary}
\email{roed.math@gmail.com}
\usepackage[utf8]{inputenc}
\renewcommand{\baselinestretch}{1.2}
\usepackage[notcite,color]{showkeys}
\usepackage{hyperref}
\usepackage{geometry}
\usepackage{amsthm}
\usepackage{amsmath}
\usepackage{amssymb}
%\usepackage[shortalphabetic]{amsrefs}
\usepackage[alphabetic]{amsrefs}
\renewcommand\MR{\relax}
\usepackage{xypic}
\usepackage{textcomp}
\usepackage{mathrsfs}
\usepackage{yfonts}
\newcommand{\mathswab}[1]{\operatorname{\textswab{#1}}}
\usepackage[T1]{fontenc}
\usepackage{tikz}
\usetikzlibrary{shapes,arrows}
\usepackage{manfnt}

@@

The main result of this paper is a canonical isomorphism
\[
\CSiso{\mathswab{T}_d} 
\iso
\Hom_{< d}(T(K),\EEx)
\] 
between the Picard group of the category of character sheaves on
$\mathswab{T}_d$ and the group of characters $T(K) \to \EEx$ of
depth at most $d$.  Since these isomorphisms are compatible with
respect to $d$, we also .....  \Clifton{I'll come back to working on
  this when we're closer to being finished. I'd be just as happy if
  you took this cup from my lips, though.}  
%In particular, by
%specializing to the case $T= \Gm{K}$ and by
%choosing an isomorphism $\EE \approx \CC$ (unnatural though it may
%be), we arrive at a model for the group of quasi-characters of
%$K^\times$: the monoidal category of character sheaves on the
%Greenberg transform of the Neron model of
%$\Gm{K}$.

@@

Consider the short exact sequence in the category of smooth group
schemes, locally of finite type over $\Fq$, defining the component
group scheme for $G$:
 \begin{equation}\label{eq:pi-1}
   \xymatrix{
     0 \ar[r] & G^0 \ar[r] & G \ar[r] & \pi_0(G) \ar[r] & 0.
    }
 \end{equation}
Since $\pi_0(G)$ is an étale group scheme locally of finite type over $\Fq$, 
it follows from Proposition~\ref{prop:pullback} that \eqref{eq:pi-1}defines a sequence of functors
 \[
  \xymatrix{
\CS(0) \ar[r] & \CS(\pi_0(G)) \ar[r] & \CS(G) \ar[r] & \CS(G^0) \ar[r] & \CS(0).
  }
 \]
We will see that

\section{Bounded character sheaves}

[Introduce category $\CS_0(G)$]

@@

  The sequence of character groups is left-exact: by
  Proposition~\ref{prop:pullback}, it is dual to the exact sequence of
  abelian groups
  \begin{equation}\label{eq:pi1}
    \xymatrix{
      1 \ar[r] & G^0(\Fq) \ar[r] & G(\Fq) \ar[r] & \pi_0(G)(\Fq) \ar[r] & 0;
    }
  \end{equation}
  since $\Hom(\ - \ ,\EEx)$ is left-exact, the sequence of
  character groups is left exact.
